---
title: "COVID 19 data visualisation"
# subtitle: ""
author: "Kamran Khan"
institute: "Institute of Health Informatics"
date: ""
output:
  xaringan::moon_reader:
    css:
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs   #creates directory for libraries
    seal: false      # false : custom title slide
    nature:
      highlightStyle: googlecode   #highlighting syntax for code 
      highlightLines: true         # true: enables code line highlighting
      highlightLanguage: ["r"]     # language to highlight
      countIncrementalSlides: false  # false: disables counting of incremental slides
      ratio: "16:9"                  # 4:3 for standard size
    includes:
      after_body: css/insert-logo.html   # add logo
---

```{r , include = FALSE}
library(knitr)
library(tidyverse)
library(nhsrtheme)
library(xaringanExtra)
library(survival)
xaringanExtra::use_panelset()
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.52,
               fig.height = 4,
               dpi = 300)
xaringanExtra::use_tile_view()
# use_share_again()
# xaringanExtra::style_share_again(share_buttons = c("twitter", "linkedin", "pocket"))



# uncomment the following lines if you want to use the NHS-R theme colours by default
scale_fill_continuous <- partial(scale_fill_nhs, discrete = FALSE)
scale_fill_discrete <- partial(scale_fill_nhs, discrete = TRUE)
scale_colour_continuous <- partial(scale_colour_nhs, discrete = FALSE)
scale_colour_discrete <- partial(scale_colour_nhs, discrete = TRUE)
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, middle, center

# COVID 19 cases and vaccinations in the UK

---


# This next slide shows visualisation using the dataset published by Our World in Data, and gives an overview of Covid and vaccination trends in the UK.

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      autodep = TRUE, fig.retina = 2,	dpi = 140,
                      fig.width = 7.5, fig.height = 4)

options(scipen = 999)
library(tidyverse)
library(plotly)
library(zoo)
library(lubridate)
library(sf)
library(rnaturalearth)

UK <- read_csv("https://covid.ourworldindata.org/data/owid-covid-data.csv") %>%
  filter(location == "United Kingdom") %>%
  drop_na(new_cases_smoothed) %>%
  select(where(~!all(is.na(.x)))) # Drop columns that contain all NA values
```

```{r}
cvv <- ggplot(UK, aes(x = date)) +
  geom_point(aes(y = new_cases, color = "Cases"), size = 0.75, shape = 21) +
  geom_point(aes(y = new_vaccinations, color = "Vaccinations"), size = 0.75, shape = 21) +
  geom_line(aes(y = new_cases_smoothed, color = "Cases(trend)"), size = 1) +
  geom_line(aes(y = new_vaccinations_smoothed, color = "Vaccinations(trend)"), size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Cases(trend)" = "darkblue", "Vaccinations(trend)" = "palegreen4",
                                "Cases" = "skyblue1", "Vaccinations" = "darkseagreen")) +
  guides(color = guide_legend(override.aes = list(linetype = c("Cases(trend)" = 1,
                                                               "Vaccinations(trend)" = 1,
                                                               "Cases" = 0,
                                                               "Vaccinations" = 0),
                                                  shape = c("Cases(trend)" = NA,
                                                            "Vaccinations(trend)" = NA,
                                                            "Cases" = 21,
                                                            "Vaccinations" = 21)))) +
  labs(title = "Covid-19 daily cases and vaccinations in the UK",
       x = "Date",
       y = "Daily cases & vaccinations (log10 scale)",
       color = NULL, caption = "Data: OWID") +
  scale_x_date(date_breaks = "4 month") +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") +
  scale_y_continuous(trans="log10")
ggplotly(cvv) %>%
  layout(hovermode = "x", legend = list(orientation = "h", xanchor = "center", x = 0.5, y = -0.1))
```


---



class: inverse, middle, center

## Vaccination progress

---
```{r}
## Vaccination progress

# Find out the rows where the second dose data are NAs when first dose were given at the start of the vaccination process
rows <- which(is.na(UK$people_fully_vaccinated) & !is.na(UK$people_vaccinated))
UK[rows, "people_fully_vaccinated"] = 0  # Change the NA values to 0

vaccine <- UK%>%
  mutate(`First dose` = round(people_vaccinated / population * 100, 3),
         `Fully vaccinated` = round(people_fully_vaccinated / population  * 100, 3)) %>%
  select(date, `First dose`, `Fully vaccinated`) %>%
  drop_na(`First dose`) %>%
  gather("doses", "Population share", -c(date)) %>%
  mutate(doses = factor(doses))

vac <- ggplot(data = vaccine, aes(x = date, y = `Population share`, fill = doses)) +
  geom_area(position = "identity") +
  theme_classic() +
  scale_fill_brewer(palette = "Green") +
  scale_x_date(date_breaks = "2 month") +
  labs(title = "Covid-19 vaccination progress in the UK",
       x = "Date", y = "Share of Population(%)",
       fill = NULL, caption = "Data: OWID") +
  theme(plot.title = element_text(hjust = -0.25), legend.position = "bottom")
# vac +
#   transition_reveal(date) +
#   ease_aes()
ggplotly(vac) %>%
   layout(hovermode = "x", legend = list(orientation = "h", xanchor = "center", x = 0.5, y = -0.1))
```


--

