---
title: "Multi-state modelling for dementia care path"
subtitle: "Presentation subtitle"
author: "Kamran Khan"
institute: "Institute of Health Informatics"
date: "Presentation Date"
output:
  xaringan::moon_reader:
    css:
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs   #creates directory for libraries
    seal: false      # false : custom title slide
    nature:
      highlightStyle: googlecode   #highlighting syntax for code 
      highlightLines: true         # true: enables code line highlighting
      highlightLanguage: ["r"]     # language to highlight
      countIncrementalSlides: false  # false: disables counting of incremental slides
      ratio: "16:9"                  # 4:3 for standard size
    includes:
      after_body: css/insert-logo.html   # add logo
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(nhsrtheme)
library(xaringanExtra)
xaringanExtra::use_panelset()
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300)
xaringanExtra::use_tile_view()
use_share_again()
xaringanExtra::style_share_again(share_buttons = c("twitter", "linkedin", "pocket"))


# 
# uncomment the following lines if you want to use the NHS-R theme colours by default
# scale_fill_continuous <- partial(scale_fill_nhs, discrete = FALSE)
# scale_fill_discrete <- partial(scale_fill_nhs, discrete = TRUE)
# scale_colour_continuous <- partial(scale_colour_nhs, discrete = FALSE)
# scale_colour_discrete <- partial(scale_colour_nhs, discrete = TRUE)
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, middle, center

# An inverse slide

Often used for transitions

---

# A slide where bullets appear

--

* first point

--

* second point


???
this is for me

---
class: .left-column[write on the left side]




# slide with some text

 .right-column[Hi I was wondering what is this?]


`r emo::ji("tada")`

`r icons::fontawesome$solid$rocket`
`r icons::fontawesome$solid$brain`
`r icons::academicons$orcid`
`r icons::ionicons$flask`



```{r icon-style}
library(icons)
icon_style(fontawesome("rocket", style = "solid"), scale = 2, fill = "red")

```

---
class: middle
.center[`r emo::ji("smile")`]

---

```{r}
NHSRdatasets::LOS_model %>% 
head() %>% 
  knitr::kable(format = "html")
```

---
class: center, middle
```{r}

NHSRdatasets::LOS_model %>% 
  head() %>% 
  DT::datatable()

```

---

# Plots

.pull-right[




```{r plot-last, fig.show = 'hide'}
  NHSRdatasets::LOS_model %>%
  ggplot(aes(x = Age, y = Organisation)) +
  geom_boxplot(aes(fill = Organisation)) +
  nhsrtheme::scale_fill_nhs("highlights")
 
```

]

.pull-left[





```{r ref.label = 'plot-last', echo=TRUE}

```



]

---

# highlight code
```{r echo = TRUE}
NHSRdatasets::LOS_model %>% 
  head() #<<

x <-  1 * 2 #<<
```

---
```{r, include=FALSE}
yt <- 0

```
# Your turn # `r (yt <- yt + 1)`
Try this!
# Your turn # `r (yt <- yt + 1)` 
Check this

---

Hi my name is `r rmarkdown::metadata$author`, and welcome to `r rmarkdown::metadata$title`
---
# Tile view 
```{r}
# 
# xaringanExtra::embed_xaringan(url = "slides.html", ratio = "16:9")

```

---
# This slide has panels
#slide panels with Panelset
.panelset[
.panel[.panel-name[Tab 1]


... your content goes here...


.panel[.panel-name[Tab 2]


...your content goes here 


.panel[.panel-name[Tab 3]


 ... more stuff ...
  
  ]
  ]
  ]
  ]
  
---








